\documentclass[parskip=yes]{scrartcl}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[a4paper,portrait,margin=1in]{geometry}
\usepackage{multicol}
\pagenumbering{gobble}

\begin{document}
\begin{flushright}
	Ioan Alexandru Popa \\ Splaiul Independenței 290 \\ 060029 Bucharest \\ Romania \\ alexioanpopa11@gmail.com \\ \today
\end{flushright}
\begin{flushleft}
Mr. George Williamson \\ Recruitment Manager \\ Caracal Technology Ltd. \\ 38 Chancery Lane \\ London WC2A 1EN
\end{flushleft}

Dear Mr. Williamson,

I am a second-year student at Politehnica University of Bucharest, and would like to apply for a Junior Rust Software Engineer position with Caracal Technology, as advertised on www.linkedin.com.

Software engineering appeals to me because it brings the ability to make complex but important things more accessible to the general public. Rust is a programming language that I love because it has an expressive type system and correctness guarantees, while at the same time having no garbage collector or other overheads. I recently attended the EuroRust 2023 conference, where Caracal Technology Senior Rust Software Engineer Alfred Wheeler gave a speech, and he gave me a very positive impression on the company, and I would welcome the opportunity to work in such a close-knit team of supportive colleagues.

With a range of experiences in software development, from the many personal projects made using a variety of programming languages to contributions to various open source projects, like OpenTTD and Unikraft, I am confident that I can develop the necessary software solutions that meet the company's needs and be part of a growing team of passionate developers like me.

I enclose a copy of my CV and hope very much to be invited for interview.

Yours sincerely,

Ioan Alexandru Popa
\end{document}
